---
title: |
  | Inteligência Artificial:
subtitle: "Potencial para modelagem de variáveis florestais"
author: "Deivison Venicio Souza"
institute: "Universidade Federal do Pará (UFPA)"
date: |
  `r format(Sys.Date(),"%d/%B/%Y")` |
  Altamira, Pará
#output: revealjs::revealjs_presentation
#output: rmdshower::shower_presentation
output:
  xaringan::moon_reader:
    includes:
      after_body: my-custom.css
    css: [default, metropolis, tamu-fonts] #xaringan-themer.css 
    lib_dir: libs
    nature:
      #autoplay: 30000
      #countdown: 60000
      #titleSlideClass: [top, left, inverse]
      highlightStyle: idea #monokai
      highlightLines: true
      highlightLanguage: r
      countIncrementalSlides: false
      ratio: "16:9"
    seal: true
---
Imagem de <a href="https://pixabay.com/pt/users/cablemarder-7142084/?utm_source=link-attribution&amp;utm_medium=referral&amp;utm_campaign=image&amp;utm_content=2987303">cablemarder</a> por <a href="https://pixabay.com/pt/?utm_source=link-attribution&amp;utm_medium=referral&amp;utm_campaign=image&amp;utm_content=2987303">Pixabay</a>

name: toc

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan

### /ʃaː.'riŋ.ɡan/

---
class: inverse, center, middle

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](http://slides.yihui.org/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---
background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
class: center, bottom, inverse

# You only live once!

---

# Hello Ninja

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

# remark.js

You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to

- create a new slide (Markdown syntax<sup>*</sup> and slide properties);

- format a slide (e.g. text alignment);

- configure the slideshow;

- and use the presentation (keyboard shortcuts).

It is important to be familiar with remark.js before you can understand the options in **xaringan**.

.footnote[[*] It is different with Pandoc's Markdown! It is limited but should be enough for presentation purposes. Come on... You do not need a slide for the Table of Contents! Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]

---

